Symmetric Circuits for Rank Gates

### 2018-03-23 sections/introduction.tex
Minor revisions to Sections 1 and 2.

Another crucial ingredient in the proof of Anderson and Dawar is that
we can eliminate redundancy in the circuit $C_n$ by making it
\emph{rigid}.  That is, we can ensure that the \emph{only}
automorphisms of $C_n$ are those that are induced by permutations of
$[n]$.  Here we face the difficulty that identifying the symmetries
and eliminating redundancy in a circuit that involves gates computing
$\tau$-invariant functions requires us to solve the isomorphism
problem for $\tau$-structures.  This is a hard problem (or, at least,
one that we do not know how to solve efficiently) even when the
$\tau$-structures are $0$-$1$-matrices.  We overcome this difficulty
by placing a further restriction on circuits that we call
\emph{transparency}.  Circuits satisfying this condition have the
property that their lack of redundancy is transparent.  We explore
this condition and its consequences in Section~\ref{sec:transparent}.

In the characterization of $\FPC$, the translation from formulas into
families of circuits is easy and, indeed, standard.  In our case, we
have to show that formulas of $\FPR$ translate into uniform families of
circuits using rank-threshold gates that are symmetric and
transparent.  This is somewhat more involved technically and the
details are presented in Section~\ref{sec:formulas-to-circuits}.
Finally, with all the tools in place, the translation of such
$\PT$-uniform families of circuits into formulas of $\FPR$ given in Section~\ref{sec:circuits-to-formulas} completes
the characterization.

\begin{remark}
G: Should we also talk about the fact that the work done in
Section~\ref{sec:circuits-to-formulas} is also novel?
\end{remark}

>>>>

Another crucial ingredient in the proof of Anderson and Dawar is that
we can eliminate redundancy in the circuit $C_n$ by making it
\emph{rigid}.  That is, we can ensure that the \emph{only}
automorphisms of $C_n$ are those that are induced by permutations of
$[n]$.  Here we face the difficulty that identifying the symmetries
and eliminating redundancy in a circuit that involves gates computing
$\tau$-invariant functions requires us to solve the isomorphism
problem for $\tau$-structures.  This is a hard problem (or, at least,
one that we do not know how to solve efficiently) even when the
$\tau$-structures are $0$-$1$-matrices.  We overcome this difficulty
by placing a further restriction on circuits that we call
\emph{transparency}.  Circuits satisfying this condition have the
property that their lack of redundancy is transparent.  We explore
this condition and its consequences in Section~\ref{sec:transparent},
where we also demonstrate that something like this requrement is
necessary.  Natural weakenings of this requirement yield circuits in
which deciding symmetry seems hard.

In the characterization of $\FPC$, the translation from formulas into
families of circuits is easy and, indeed, standard.  In our case, we
have to show that formulas of $\FPR$ translate into uniform families of
circuits using rank-threshold gates that are symmetric and
transparent.  This is somewhat more involved technically and the
details are presented in Section~\ref{sec:formulas-to-circuits}.
Finally, with all these tools in place, the translation of such
$\PT$-uniform families of circuits into formulas of $\FPR$ given in Section~\ref{sec:circuits-to-formulas} completes
the characterization.  This still requires substantial new
techniques.  The translation of circuits to formulas
in~\cite{AndersonD17} relies on the fact that in order to evaluate a
gate computing a symmetric Boolean function, it suffices to count the number
of inputs that evaluate to true and there is a bijection between the
orbits of a gate and tuple assignments to its support.  When counting
is no longer sufficient, this bijection has to preserve more structure
and demonstrating this in the case of matrices requires new insight.
